                         ---
title: "House Sale Data"
author: "Awhy"
date: "11/02/2020"
output: pdf_document: default
---

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)

```
```{r}
require(pacman)
pacman::p_load(ggplot2, ggvis, plyr,tidyverse, data.table, lubridate, cowplot, corrplot, lubridate,markdown)

```
## R Markdown
```{r df}

df<- read.csv(file = "train.csv", stringsAsFactors = FALSE, header = TRUE)

```
```{r}
head (df)

dfw <- df[,c(3,4,5,6,10,13,14,16,17,19,20,41,42,54,74,79,81 )]
head(dfw) 

```
```{r}
na.cols <- which(colSums(is.na(dfw)) > 0)
na.cols <- sort(colSums(sapply(dfw[na.cols], is.na)), decreasing = TRUE)
paste('There are', length(na.cols), 'columns with missing values')
na.cols
dfw.MedLF <- median(dfw$LotFrontage, na.rm = TRUE)
dfw.MedLF
dfw[is.na(dfw$LotFrontage), "LotFrontage"] <- dfw.MedLF
head(dfw$LotFrontage) 

```
###################################################
#### Basic Exploratory Data Analysis
###################################################
### what constitute our data/ characteristics of the data
```{r, echo= FALSE}
dim(dfw)
colnames(dfw)
str(dfw)
summary(dfw)

dfw$Yearsold <- 2020-dfw$YearBuilt
dfwmsz <- as.data.frame(dfw$MSZoning)
dfwlf <- as.data.frame(dfw$LotFrontage)
dfwlta <- as.data.frame(dfw$LotArea)
dfwStreet <- as.data.frame(dfw$Street)
dfwu <- as.data.frame(dfw$Utilities)
dfwn <- as.data.frame(dfw$Neighborhood)
dfwc <- as.data.frame(dfw$Condition1)
dfwbt <- as.data.frame(dfw$BldgType)
dfwhs <- as.data.frame(dfw$HouseStyle)
dfwoc <- as.data.frame(dfw$OverallCond)
dfwhqc <- as.data.frame(dfw$HeatingQC)
dfwca <- as.data.frame(dfw$CentralAir)
dfwkq <- as.data.frame(dfw$KitchenQual)
dfwfence <- as.data.frame(dfw$Fence)
dfwst <- as.data.frame(dfw$SaleType)
dfwsp <- as.data.frame(dfw$SalePrice)
min(dfw$Yearsold)
max(dfw$Yearsold)
dfw$ygrp <- cut(dfw$Yearsold, seq(10,148, 10))
head (dfw$ygrp) 
```
#### correlation
### get numeric columns

```{r, echo=FALSE}

plot (dfwmsz, xlab = "MSZoning: Identifies the general zoning classification of the sale.")


```
###MSZoning: Identifies the general zoning classification of the sale.
 ###RL =	Residential Low Density house most of the houses
```{r, echo= FALSE}
plot (dfwlf, xlab = "Linear feet of street connected to property")

```
###LotFrontage: Linear feet of street connected to property
```{r, echo= FALSE}
plot (dfwlta, xlab = "LotArea: Lot size in square feet")

```
```{r, echo= FALSE}
plot (dfwStreet, xlab = "Street: Type of road access to property")

```
##Street: Type of road access to property (Grvl=Gravel,Pave =	Paved)
```{r, echo= FALSE}
plot (dfwu, xlab = "Utilities: Type of utilities available")

```

###Utilities: Type of utilities available
		###(AllPub	All public Utilities (E,G,W,& S)	
       ###NoSewr	= Electricity, Gas, and Water (Septic Tank)
       ###NoSeWa	= Electricity and Gas Only, ELO=	Electricity only)	
```{r, echo=FALSE}
plot (dfwn, xlab = "Neighborhood: Physical locations within Ames city limits")

```
###Neighborhood: Physical locations within Ames city limits
###(Blmngtn = Bloomington Heights,Blueste =	Bluestem,BrDale	= Briardale, BrkSide=Brookside, 
###ClearCr =	Clear Creek, CollgCr= College Creek, Crawfor =	Crawford, Edwards=Edwards, ###Gilbert=Gilbert,IDOTRR=Iowa DOT and Rail Road, MeadowV=Meadow Village, Mitchel=Mitchell, ###Names=North Ames, NoRidge=Northridge, NPkVill=Northpark Villa, NridgHt=Northridge ###Heights,NWAme=Northwest Ames, OldTown = Old Town, SWISU=South & West of Iowa State University, ###Sawyer, SawyerW	= Sawyer West, Somerst	= Somerset, StoneBr =	Stone Brook, Timber	= Timberland,	###Veenker)
```{r, echo=FALSE}
plot (dfwc, xlab = "Condition1: Proximity to various conditions")
```
###Condition1: Proximity to various conditions
###(Artery	Adjacent to arterial street,Feedr	Adjacent to feeder street, Norm	Normal, RRNn	Within ###200'of North-South Railroad, RRAn	Adjacent to North-South Railroad, PosN	Near positive off-site ###feature--park, greenbelt, etc., PosA	Adjacent to postive off-site feature, RRNe	Within 200' of ###East-West Railroad, RRAe	Adjacent to East-West Railroad)
```{r, echo=FALSE}
plot (dfwbt, xlab = "BldgType: Type of dwelling")

```
###BldgType: Type of dwelling
###1Fam	Single-family Detached	
###2FmCon	Two-family Conversion; originally built as one-family dwelling
###Duplx	Duplex
###TwnhsE	Townhouse End Unit
###TwnhsI	Townhouse Inside Unit
```{r, echo=FALSE}
plot (dfwhs, xlab = "HouseStyle: Style of dwelling")

```
###HouseStyle: Style of dwelling
###1Story	One story
###1.5Fin	One and one-half story: 2nd level finished
###1.5Unf	One and one-half story: 2nd level unfinished
###2Story	Two story
###2.5Fin	Two and one-half story: 2nd level finished
###2.5Unf	Two and one-half story: 2nd level unfinished
###SFoyer	Split Foyer
###SLvl	Split Level
```{r, echo=FALSE}
plot (dfwoc, xlab = "OverallCond: Rates the overall condition of the house")

```
###OverallCond: Rates the overall condition of the house
###10	Very Excellent
###9	Excellent
###8	Very Good
###7	Good
###6	Above Average	
###5	Average
###4	Below Average	
###3	Fair
###2	Poor
###1	Very Poor
```{r, echo=FALSE}
plot (dfwhqc, xlab = "HeatingQC: Heating quality and condition")

```
###HeatingQC: Heating quality and condition
### Ex	Excellent
### Gd	Good
### TA	Average/Typical
### Fa	Fair
### Po	Poor
```{r, echo=FALSE}
plot (dfwca, xlab = "CentralAir: Central air conditioning")

```
###CentralAir: Central air conditioning
###       N	No
###       Y	Yes
```{r, echo=FALSE}
plot (dfwkq, xlab = "KitchenQual: Kitchen quality")

```
###KitchenQual: Kitchen quality
###Ex	Excellent
###Gd	Good
###TA	Typical/Average
###Fa	Fair
###Po	Poor
```{r, echo=FALSE}
plot (dfwfence, xlab = "Fence: Fence quality")

```
###Fence: Fence quality
###GdPrv	Good Privacy
###MnPrv	Minimum Privacy
###GdWo	Good Wood
###MnWw	Minimum Wood/Wire
####NA	No Fence
```{r}
plot (dfwst, xlab = "SaleType: Type of sale")

```
###SaleType: Type of sale
###WD 	Warranty Deed - Conventional
###CWD	Warranty Deed - Cash
###VWD	Warranty Deed - VA Loan
###New	Home just constructed and sold
###COD	Court Officer Deed/Estate
###Con	Contract 15% Down payment regular terms
###ConLw	Contract Low Down payment and low interest
###ConLI	Contract Low Interest
###ConLD	Contract Low Down
###Oth	Other
```{r}
plot (dfwsp, xlab = "SalePrice")

```
###Cost of Selling
```{r}
plot(dfw$ygrp, xlab = " Amount of Years")

```
### The age of the building
```{r, echo=FALSE}
ggplot(dfw, aes(x=SalePrice)) +
  theme_bw() + 
  geom_histogram(bins = 20) +
  labs ( y="Count ", 
        x = "Sales Price")

#Sale Price by 10 years grouping
ggplot(data=dfw, aes(x=ygrp, y=SalePrice)) +
  geom_bar(stat="identity")

#Sale Price by street
ggplot(data=dfw, aes(x= Street, y=SalePrice)) +
  geom_bar(stat="identity")

```